Meesters TODO List

### 2023-04-15 files/Chapter2/generalvibrationmodel.tex
temp changes, pulling

Therefore $\displaystyle \frac{T''(t)}{T(t)}$ must be a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. Then the function $T$ satisfies the following differential equation
\begin{eqnarray}
	\ddot{T} + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
\end{eqnarray}

The following problem is also obtained and is called an eigenvalue problem. \sout{For the pinned-pinned beam, this eigenvalue problem is referred to as Problem T-1E.}
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in \mathbb{R}$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.

>>>>

Therefore $\displaystyle \frac{T''(t)}{T(t)}$ is a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. This can also be written as the following differential equation
\begin{eqnarray}
	\ddot{T} + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
\end{eqnarray}

To determine if such a number $\lambda$ exists, the following eigenvalue problem is considered.

\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in \mathbb{R}$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.
